Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Insect Populations and Diseases?

### 2017-09-20 analysis/paper/paper.Rmd
Add eps file and edit title of paper
Add metadata and apps abstract to analysis directory

---
title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Pests and Diseases?
author:
  - name: A.H. Sparks
    email: adam.sparks@usq.edu.au
    affiliation: University of Southern Queensland
    corresponding: adam.sparks@usq.edu.au
  - name: N.P. Castilla
    email: n.castilla@irri.org
    affiliation: International Rice Research Institute
  - name: B.A.R. Hadi
    email: b.hadi@irri.org
    affiliation: International Rice Research Institute
  - name: B.O. Sander
    email: b.sander@irri.org
    affiliation: International Rice Research Institute
address:
  - code: University of Southern Queensland
    address: Centre for Crop Health, West Street, Toowoomba, Queensland, Australia, 4350
  - code: International Rice Research Institute
    address: Los Baños, Laguna, Philippines, 4031
abstract: |
  Water and nitrogen management play vital roles in rice production. However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels. To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and traditional flood irrigation regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016. Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. We were unable to detect any differences in disease in either experiment due to irrigation regime, N rates or the interaction of the two treatments in either season. This suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence. We suggest that further cross-cutting research in this area is warranted.

@@

The sub plot treatments were different rates of nitrogen…

@@

>>>>

---
title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Insect Populations and Diseases?
author:
  - name: A.H. Sparks
    email: adam.sparks@usq.edu.au
    affiliation: University of Southern Queensland
    corresponding: adam.sparks@usq.edu.au
  - name: N.P. Castilla
    email: n.castilla@irri.org
    affiliation: International Rice Research Institute
  - name: B.A.R. Hadi
    email: b.hadi@irri.org
    affiliation: International Rice Research Institute
  - name: B.O. Sander
    email: b.sander@irri.org
    affiliation: International Rice Research Institute
address:
  - code: University of Southern Queensland
    address: Centre for Crop Health, West Street, Toowoomba, Queensland, Australia, 4350
  - code: International Rice Research Institute
    address: Los Baños, Laguna, Philippines, 4031
abstract: |
  Water and nitrogen management play vital roles in rice production. However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels. To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and traditional flood irrigation regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016. Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. We were unable to detect any differences in disease in either experiment due to irrigation regime, N rates or the interaction of the two treatments in either season. This suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence. We suggest that further cross-cutting research in this area is warranted.

@@

The subplot treatments were different rates of nitrogen…

The plots were inoculated using...

@@

The plots were inoculated using...
